---
title: "p8105_hw1_yl5505"
author: "Yan Li"
date: "2024-09-21"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(palmerpenguins)
```

# Problem 1

```{r }

data("penguins", package = "palmerpenguins")

```

## short description of the penguins dataset

The penguins dataset contains observational data, it includes the following important variables:

* species: The species of penguins (Adelie, Chinstrap, Gentoo).
* island: The island where the penguins were observed (Torgersen, Biscoe, Dream).
* bill_length_mm: The length of the penguins' bills in millimeters.
* bill_depth_mm: The depth of the penguins' bills in millimeters.
* flipper_length_mm: The length of the penguins' flippers in millimeters.
* body_mass_g: The mass of the penguins in grams.
* sex: The sex of the penguins (male, female).

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length across all penguins in the dataset is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.







