---
title: "p8105_hw1_yl5505"
author: "Yan Li"
date: "2024-09-21"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

# Problem 1

## Load the penguins dataset
```{r }

data("penguins", package = "palmerpenguins")

```

## Short description of the penguins dataset

The penguins dataset contains observational data, it includes 8 variables:

1. species: The species of penguins (Adelie, Chinstrap, Gentoo).
1. island: The island where the penguins were observed (Torgersen, Biscoe, Dream).
1. bill_length_mm: The length of the penguins' bills in millimeters.
1. bill_depth_mm: The depth of the penguins' bills in millimeters.
1. flipper_length_mm: The length of the penguins' flippers in millimeters.
1. body_mass_g: The mass of the penguins in grams.
1. sex: The sex of the penguins (male, female).
1. year: The year in which the penguin observations were recorded.

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length across all penguins in the dataset is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot of Flipper Length vs Bill Length

```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
```

## Save the plot

```{r export}
ggsave("penguin_scatterpplot.pdf")
```

# Problem 2

## Create data frame

```{r}
  p2_data=tibble(
  random_sample = rnorm(10,sd=1), 
  logic_vector = random_sample > 0, 
  character_vector = c("aa","bb","cc","dd","ee","ff","gg","hh","ii","jj"),
  factor_vector = factor(c("low", "medium", "high", "low", "high", "medium", "low", "high", "medium", "low"))
  )
```









